Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*

### 2024-02-02 Code/Manuscript_O2.Rmd
Added figures from the OceanProteinProchloro repository.

---
title: "Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*"
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1,2
  - name: Maximilian Berthold
    affil: 1
  - name: Naaman Omar
    affil: 1
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: ''
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
date: "`r format(Sys.Date())`"
output:
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchlor", "Output")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")

@@

@@

>>>>

---
title: "Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*"
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1,2
  - name: Maximilian Berthold
    affil: 1
  - name: Naaman Omar
    affil: 1
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: ''
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchloro", "Output")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")

@@

```{r ProchloroElectronTrans, fig.cap = ProchloroElectronTrans_cap , fig.height = 20, fig.width = 10, echo = FALSE}

ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal. X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
                       "Rows are...",
                       "Columns are...",

knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroElectronTrans.png"))
```

@@

```{r ProchloroMetabDepthO2, fig.cap = ProchloroMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}

ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
                       "Rows are...",
                       "Columns are...",

knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroMetabDepthO2.png"))
```
